Analysis

### 2022-06-06 FIMO_processing.Rmd
Process mouse liftOver data
Additional summary of mm MA0139 data

# Human data hg18

@@

@@

```{r}
# for file in `find . -type f -name "*MA0139*"`; do
#   echo $file
#   newfile=`echo $file | sed 's/MA0139/JASPAR2022_MA0139/'`
#   echo $newfile
#   mv $file $newfile
# done
# 
# Output files
fileNameOut1 <- file.path(dir_data, "log_PWMs.csv")
if (file.exists(fileNameOut1)) { file.remove(fileNameOut1) }
# Defined from FIMO_EDA
pval_threshold <- 1e-6
files <- list.files(dir_data, pattern = "*.bed", full.names = TRUE)
for (fil in files) {
  print(basename(fil) %>% str_remove(., ".bed"))
  mtx <- read_tsv(fil, col_names = FALSE, col_types = c("ciicdciddc"))
  colnames(mtx) <- c("seqnames", "start", "end", "name", "score", "strand", "width", "pvalue", "qvalue", "sequence")
  gr <- makeGRangesFromDataFrame(mtx, keep.extra.columns = TRUE)
  # Summary
  summary_to_save <- data.frame(File = basename(fil) %>% str_remove(., ".bed"),
                                Assembly = strsplit(basename(fil), ".", fixed = TRUE)[[1]][1],
                                `All (p-value threshold 1e-4)` = length(gr),
                                `Reduced (p-value threshold 1e-4)` = length(reduce(gr)),
                                `All (p-value threshold 1e-6)` = length(gr[gr$pvalue < pval_threshold]),
                                `Reduced (p-value threshold 1e-6)` = length(reduce(gr[gr$pvalue < pval_threshold])) )
  write_csv(summary_to_save, fileNameOut1, append = TRUE)
  gc()
}
```

>>>>

# Human data liftOver

@@

# Mouse data liftOver

```{r hg18}
for (gen in c(genome_mouse)) {
  for (mot in "MA0139.1") {
    print(paste(gen, paste0("JASPAR2022_", mot), sep = "."))
    combine_fimo(motif = mot, genome_id = gen, chromosomes = chromosome_mouse)
  }
}
```

@@

```{r}
# for file in `find . -type f -name "*MA0139*"`; do
#   echo $file
#   newfile=`echo $file | sed 's/MA0139/JASPAR2022_MA0139/'`
#   echo $newfile
#   mv $file $newfile
# done
# 
# Output files
fileNameOut1 <- file.path(dir_data, "log_PWMs.csv")
if (file.exists(fileNameOut1)) { file.remove(fileNameOut1) }
# Defined from FIMO_EDA
pval_threshold <- 1e-6
files <- list.files(dir_data, pattern = "*MA0139.1.bed", full.names = TRUE)
files <- files[grepl("mm", files)]
for (fil in files) {
  print(basename(fil) %>% str_remove(., ".bed"))
  mtx <- read_tsv(fil, col_names = FALSE, col_types = c("ciicdciddc"))
  colnames(mtx) <- c("seqnames", "start", "end", "name", "score", "strand", "width", "pvalue", "qvalue", "sequence")
  gr <- makeGRangesFromDataFrame(mtx, keep.extra.columns = TRUE)
  # Summary
  summary_to_save <- data.frame(File = basename(fil) %>% str_remove(., ".bed"),
                                Assembly = strsplit(basename(fil), ".", fixed = TRUE)[[1]][1],
                                `All (p-value threshold 1e-4)` = length(gr),
                                `Reduced (p-value threshold 1e-4)` = length(reduce(gr)),
                                `All (p-value threshold 1e-6)` = length(gr[gr$pvalue < pval_threshold]),
                                `Reduced (p-value threshold 1e-6)` = length(reduce(gr[gr$pvalue < pval_threshold])) )
  write_csv(summary_to_save, fileNameOut1, append = TRUE)
  gc()
}
```
